\Large Analyzing the Supreme Court Citation Network

### 2017-11-22 Tex/paper.tex
first results

\documentclass[headsepline=true, abstracton]{scrartcl}
%\usepackage[ngerman]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{enumerate}
\usepackage{verbatim}
\usepackage[a4paper,text={140mm,215mm},centering,headsep=10mm,footskip=10mm]{geometry}
\usepackage[urlcolor=black,colorlinks=true,linkcolor=black,citecolor=black,bookmarks]{hyperref}
\usepackage{aliascnt}
\usepackage{lmodern}
\usepackage{mdwlist}
\usepackage{listings}
\usepackage[activate]{pdfcprot}
\usepackage{graphicx}
\usepackage{slashed}
\usepackage{mathrsfs}
\usepackage{geometry}
\usepackage{float}
\usepackage{oldgerm}
\usepackage{setspace}
\usepackage{dsfont}
%\usepackage{mathtools}
\usepackage[all]{xy}
\usepackage{cite}
%\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{algorithm2e}
\usepackage{url}
\pagestyle{headings}
\newcommand{\myclearpage}{\clearpage}
\newcommand\independent{\protect\mathpalette{\protect\independenT}{\perp}}
\def\independenT#1#2{\mathrel{\rlap{$#1#2$}\mkern2mu{#1#2}}}
\newenvironment{gelaber}{}{}
\newenvironment{preamble}{}{}
\newcommand{\tostar}{\overset{*}{\lower0.5em\hbox{$\smash{\scriptscriptstyle\rightharpoonup}$}}}
\newtheorem{mydef}{Definition}
\newtheorem{bem}{Bemerkung}
\usepackage{tikz}
\newcommand\circlearound[1]{%
  \tikz[baseline]\node[draw,shape=circle,anchor=base] {#1} ;}

@@

 \section*{Results/Discussion}

>>>>

\documentclass[headsepline=true, abstracton]{scrartcl}
%\usepackage[ngerman]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{enumerate}
\usepackage{verbatim}
\usepackage[a4paper,text={140mm,215mm},centering,headsep=10mm,footskip=10mm]{geometry}
\usepackage[urlcolor=black,colorlinks=true,linkcolor=black,citecolor=black,bookmarks]{hyperref}
\usepackage{aliascnt}
\usepackage{lmodern}
\usepackage{mdwlist}
\usepackage{listings}
\usepackage[table,xcdraw]{xcolor}
\usepackage[activate]{pdfcprot}
\usepackage{graphicx}
\usepackage{slashed}
\usepackage{mathrsfs}
\usepackage{geometry}
\usepackage{float}
\usepackage{oldgerm}
\usepackage{setspace}
\usepackage{dsfont}
%\usepackage{mathtools}
\usepackage[all]{xy}
\usepackage{cite}
%\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{algorithm2e}
\usepackage{url}
\pagestyle{headings}
\newcommand{\myclearpage}{\clearpage}
\newcommand\independent{\protect\mathpalette{\protect\independenT}{\perp}}
\def\independenT#1#2{\mathrel{\rlap{$#1#2$}\mkern2mu{#1#2}}}
\newenvironment{gelaber}{}{}
\newenvironment{preamble}{}{}
\newcommand{\tostar}{\overset{*}{\lower0.5em\hbox{$\smash{\scriptscriptstyle\rightharpoonup}$}}}
\newtheorem{mydef}{Definition}
\newtheorem{bem}{Bemerkung}
\usepackage{tikz}
\newcommand\circlearound[1]{%
  \tikz[baseline]\node[draw,shape=circle,anchor=base] {#1} ;}

@@

 \section*{Results}
  \subsection*{Descriptive Results}
 The supreme court citation network from $1937 - 2005$ consists of $8817$ cases which got voted at 2116 different time points. The network has a total of $93,263$ ties, of which 452 are mutual. The number of triangles in the network is $211,855$. The in- and outdegree distribution is visualized in figures \ref{indegree_dist} and \ref{outdegree_dist}. The maximum indegree is $190$ and the maximum outdegree is $159$.

\begin{figure}
\includegraphics[scale=0.5]{degree_distribution}
\caption{The in- and outdegree distribution of the Supreme Court Citation Network from 1937 - 2005. There are cases with an indegree >50, but they are not captured in this figure.}
 \label{degree_dist}
\vspace{-.25cm}
\end{figure}

\subsection*{Inferential Results}

\begin{table}[]
\centering
\begin{tabular}{|
>{\columncolor[HTML]{C0C0C0}}l |l|l|l|}
\hline
{\color[HTML]{333333} } & \cellcolor[HTML]{C0C0C0}{\color[HTML]{333333} Estimate} & \cellcolor[HTML]{C0C0C0}{\color[HTML]{333333} Lower Bound} & \cellcolor[HTML]{C0C0C0}{\color[HTML]{333333} Upper Bound} \\ \hline
Edges                   & -5.364                                                 & -5.411                                                     & -4.155                                                     \\ \hline
Instar(2)               & 0.031                                                   & 0.025                                                      & 0.037                                                      \\ \hline
Outstar(2)              & 0.016                                                   & -0.004                                                      & 0.017                                                      \\ \hline
Mutual                  & 4.472                                                   & 3.821                                                 & 5.069                                                      \\ \hline
Triangle                & 1.275                                                   & 1.194                                                      & 1.401                                                      \\ \hline
MQ Score                & 0.174                                                   & 0.082                                                      & 0.244                                                      \\ \hline
Same Issue Area         & 1.113                                                   & 0.972                                                      & 1.152                                                      \\ \hline
Year Difference         & -0.092                                                   & -0.114                                                     & -0.085                                                          \\ \hline
\end{tabular}
\caption{Bootstrappped MPLE Results for the timep period when Fred M. Vinson was chief justice.}
\label{bootMPLE_vinson}
\end{table}

\begin{table}[]
\centering
\begin{tabular}{|
>{\columncolor[HTML]{C0C0C0}}l |l|l|l|}
\hline
{\color[HTML]{333333} } & \cellcolor[HTML]{C0C0C0}{\color[HTML]{333333} Estimate} & \cellcolor[HTML]{C0C0C0}{\color[HTML]{333333} Lower Bound} & \cellcolor[HTML]{C0C0C0}{\color[HTML]{333333} Upper Bound} \\ \hline
Edges                   & -3.571                                                 & -3.597                                                     & -3.460                                                     \\ \hline
Instar(2)               & 0.014                                                   & 0.013                                                      & 0.016                                                      \\ \hline
Outstar(2)              & 0.001                                                   & -0.001                                                      & 0.004                                                      \\ \hline
Mutual                  & 9.678                                                   & 8.308                                                 & 11.261                                                      \\ \hline
Triangle                & 1.526                                                   & 1.417                                                      & 1.527                                                      \\ \hline
MQ Score                & -0.0001                                                   & -0.043                                                      & 0.012                                                      \\ \hline
Same Issue Area         & 0.826                                                   & 0.718                                                      & 0.822                                                      \\ \hline
Year Difference         & -0.017                                                   & -0.018                                                     & -0.015                                                          \\ \hline
\end{tabular}
\caption{Bootstrappped MPLE Results for the timep period when William Rehnquist was chief justice.}
\label{bootMPLE_vinson}
\end{table}
